A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Beam Dynamics

### 2018-07-10 paper/theor-experiment.tex
small tweaks to tba tikz
fixing linac tikz

\begin{figure}
	\begin{tikzpicture}[every node/.style={anchor=south west,inner sep=0pt},x=1mm, y=1mm,]   
	\node (fig1) at (0,0)
	{\includegraphics[width=0.9\textwidth]{Report/awa-drawing}};
	\node[fill=white, inner sep=2pt] (txt2) at (10,-10) {$s_1$};
	\node[fill=white, inner sep=2pt, rotate=26] (txt2) at (18,19.5) {Slit};	
	\end{tikzpicture}
	\caption{High charge beam line layout at the AWA.}
	\label{awa-linac}
\end{figure}

\begin{figure}
	\begin{tikzpicture}[every node/.style={anchor=south west,inner sep=0pt},x=1mm, y=1mm,]   
	\node (fig2) at (0,0)
	{\includegraphics[width=\textwidth]{Report/tba_dogleg}};
	\node[fill=white, inner sep=2pt] (txt2) at (2,35) {$s_1$};
	\node[fill=white, inner sep=2pt] (txt2) at (14,35) {$s_2$};
	\node[fill=white, inner sep=2pt] (txt2) at (35,31) {$s_3$};
	\node[fill=white, inner sep=2pt] (txt2) at (24,50) {Septum};
	\draw [blue, ->, line width=1] (30,50) -- (30, 42);	
	\node[fill=white, inner sep=2pt] (txt2) at (5,50) {Kicker};
	\draw [blue, ->, line width=1] (10,50) -- (18, 43);
	\end{tikzpicture}
	\caption{Continuation of the high charge beam line layout at the AWA. 
		This is the the two beam acceleration section.}
	\label{awa-tba}
\end{figure}

>>>>

\begin{figure}
	\begin{tikzpicture}[every node/.style={anchor=south west,inner sep=0pt},x=1mm, y=1mm,]   
	\node (fig1) at (0,0)
	{\includegraphics[width=\textwidth]{Report/awa-drawing}};
	\node[fill=white, inner sep=2pt] (txt2) at (125,10) {$s_2$};
	\node[fill=white, inner sep=2pt] (txt2) at (112,8) {$s_1$};
	\node[fill=white, inner sep=2pt] (txt2) at (115,30) {Kicker};
	\draw [blue, ->, line width=1] (120,30) -- (120, 23);	
	\end{tikzpicture}
	\caption{Side view of the high charge linac at the AWA. 
		All hardware in this drawing is currently installed.}
	\label{awa-linac}
\end{figure}

\begin{figure}
	\begin{tikzpicture}[every node/.style={anchor=south west,inner sep=0pt},x=1mm, y=1mm,]   
	\node (fig2) at (0,0)
	{\includegraphics[width=\textwidth]{Report/tba_dogleg}};
	\node[fill=white, inner sep=2pt] (txt2) at (2,35) {$s_1$};
	\node[fill=white, inner sep=2pt] (txt2) at (14,35) {$s_2$};
	\node[fill=white, inner sep=2pt] (txt2) at (33,31) {$s_3$};
	\node[fill=white, inner sep=2pt] (txt2) at (24,50) {Septum};
	\draw [blue, ->, line width=1] (30,50) -- (30, 42);	
	\node[fill=white, inner sep=2pt] (txt2) at (3,50) {Kicker};
	\draw [blue, ->, line width=1] (9.5,50) -- (9.5, 43);
	\end{tikzpicture}
	\caption{Continuation of the high charge beam line layout at the AWA, top view. 
		This is the proposed two beam acceleration section.}
	\label{awa-tba}
\end{figure}
